Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-04 mu/article/article-revtex.tex
Converting documentclass from article t revtex4-1.

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
\raggedbottom           % don't add extra vertical space
\begin{comment}
\pagestyle{empty}       % use if page numbers not wanted
\end{comment}

@@

\title{Introduction to \LaTeX}
\author{Harvey Gould}
\affiliation{Clark University, Department of Physics, Worcester, MA 01610}
\affiliation{Boston University, Department of Physics, Boston, MA 02215}

\date{16 June 2013}

\begin{abstract}
We give a brief introduction to the use of \LaTeX\ in the context of REVTeX~4.1.
\end{abstract}

>>>>

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
\usepackage{blindtext}  % fill text

\raggedbottom           % don't add extra vertical space
\pagestyle{empty}       % use if page numbers not wanted

@@

\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
\author{Reinaldo Zapata-Pe\~na, Bernardo S. Mendoza, Anatoli I. Shkrebtii}
\affiliation{Centro de Investigaciones en \'Optica, Le\'on, Guanajuato 37150, M\'exico}
\affiliation{University of Ontario, Institute of Technology, Oshawa, ON, L1H 7L7, Canada}

\date{\today}

\begin{abstract}
\blindtext
\end{abstract}
